rethinking and the 5 genera

### 2021-04-14 scripts/43_comparisons_3.Rmd
although slow but Im progressing

sub_phenos <- pheno %>% 
  split(., list(.$center, .$pheno)) %>% 
  purrr::imap(~ filter(.data = ., value != 'not_assessed'))
```

@@

cmds <- tibble(
  fns = fns
) %>% 
  mutate(format_cmd = str_glue('format_input.py {fns}  {fns}.in -c 1 -u 2')) %>% 
  mutate(run_cmd = str_glue('run_lefse.py {fns}.in  {fns}.res')) %>% 
  mutate(plot_cmd = str_glue('plot_res.py {fns}.res {fns}.png  --feature_font_size 4 --width 10 --dpi 300 --title {fns}')) %>% 
  select(-fns) %>% 
  gather() %>% 
  select(value) %>% 
  write_csv('../data/shotgun_output/humann3/lefse_run_cmd.sh', col_names = F)
```

>>>>

sub_phenos <- pheno %>% 
  split(., list(.$center, .$pheno)) %>% 
  purrr::imap(~ filter(.data = ., value != 'not_assessed'))

cur %>% 
  write_csv('../data/shotgun_pheno/final_comprehensive_updated_simple.csv')
```

@@

cmds <- tibble(
  fns = fns
) %>% 
  mutate(format_cmd = str_glue('format_input.py {fns}  {fns}.in -c 1 -u 2')) %>% 
  mutate(run_cmd = str_glue('run_lefse.py {fns}.in  {fns}.res')) %>% 
  mutate(plot_cmd = str_glue('plot_res.py {fns}.res {fns}.pdf --format pdf  --feature_font_size 4 --width 10 --dpi 300 --title {fns}')) %>% 
  select(-fns) %>% 
  gather() %>% 
  select(value) %>% 
  write_csv('../data/shotgun_output/humann3/lefse_run_cmd.sh', col_names = F)
```

### 2021-04-14 scripts/45_16s_sorting_out.Rmd
ud[ate
although slow but Im progressing

```{r}
library(tidyverse)
library(readxl)
```

@@

p <- u_meta_b %>%   
  mutate(time_group = 'Baseline') %>% 
  select(-sampleid) %>% 
  rename(sampleid = oligoid) %>% 
  select(-last_followup_day) %>% 
  mutate(center = 'P')  %>% 
  select(colnames(m))

@@

m %>% 
  count(anaerobe_targeting, cr_d100) %>% 
  ggbarplot(x = 'anaerobe_targeting', y= 'n', color = 'cr_d100', fill = 'cr_d100')
```

>>>>

```{r}
library(tidyverse)
library(readxl)
library(ggpubr)
```

@@

p <- u_meta_b %>%   
  mutate(time_group = 'Baseline') %>% 
  select(-sampleid) %>% 
  rename(sampleid = oligoid) %>% 
  select(-last_followup) %>% 
  mutate(center = 'P')  %>% 
  select(colnames(m))

@@

m %>% 
  count(anaerobe_targeting, cr_d100) %>% 
  ggbarplot(x = 'anaerobe_targeting', y= 'n', color = 'cr_d100', fill = 'cr_d100', label = TRUE)
```

### 2021-04-14 scripts/51_distance_2_healthy.Rmd
although slow but Im progressing

```{r}
# plotting
centroid_grp %>% 
  ggboxplot(x = 'groups', y = 'dist_to_centroid', add = 'jitter', xlab = '',
            ylab = 'Distance to healthy cohort', title = 'Per sampleid')  +
  stat_compare_means(comparisons= list(c('CART', 'healthy')),
            label= "p.format",
            method= 'wilcox.test',
						correct=FALSE) +
  ggsave('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/Angel_amplicon/distance_to_centroid/all_CART_compared_to_healthy.pdf')
```
```{r}
centroid_center %>% 
  ggboxplot(x = 'groups', y = 'dist_to_centroid', add = 'jitter', xlab = '',
            ylab = 'Distance to healthy cohort', title = 'Per sampleid')  +
  stat_compare_means(comparisons= list(c('M','P'), c('M', 'healthy'), c('P', 'healthy')),
            label= "p.format",
            method= 'wilcox.test',
						correct=FALSE) +
  ggsave('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/Angel_amplicon/distance_to_centroid/centers_compared_to_healthy.pdf')
```

>>>>

```{r}
# plotting
centroid_grp %>% 
  ggboxplot(x = 'groups', y = 'dist_to_centroid', add = 'jitter', xlab = '',
            ylab = 'Distance to healthy cohort', title = 'Per sampleid')  +
  stat_compare_means(comparisons= list(c('CART', 'healthy')),
            label= "p.format",
            method= 'wilcox.test',
						correct=FALSE) +
  ggsave('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/Angel_amplicon/distance_to_centroid/all_CART_compared_to_healthy.pdf')
```
```{r}
centroid_center %>% 
  ggboxplot(x = 'groups', y = 'dist_to_centroid', add = 'jitter', xlab = '',
            ylab = 'Distance to healthy cohort', title = 'Per sampleid')  +
  stat_compare_means(comparisons= list(c('M','P'), c('M', 'healthy'), c('P', 'healthy')),
            label= "p.format",
            method= 'wilcox.test',
						correct=FALSE) +
  ggsave('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/Angel_amplicon/distance_to_centroid/centers_compared_to_healthy.pdf')

centroid_center %>% 
  filter(groups == 'healthy')
```
```{r}
# dominance in healthy volunteers 
h <- get_counts_subset(healthy$sampleid)

cts <- h %>% 
  select(asv_key, sampleid, count) %>% 
  spread(key = 'sampleid', value = 'count', fill = 0) %>% 
  arrange(asv_key)

mannot <- asv_annotation_blast_ag %>% 
  filter(asv_key %in% cts$asv_key) %>% 
  mutate(ordr =  if_else(ordr == '', str_glue('of_class_{class}'), ordr),
         family =  if_else(family == '', str_glue('of_order_{ordr}'), family),
         genus =  if_else(genus == '', str_glue('of_family_{family}'), genus),
         species =  if_else(species == '', str_glue('of_genus_{genus}'), species)) 
mcts_all <- cts %>% 
  full_join(mannot %>%  select(asv_key, genus), by  = 'asv_key') %>% 
  select(-asv_key) %>% 
  gather(key = 'sampleid', value = 'count', names(.)[1]:names(.)[ncol(.) - 1]) %>% 
  group_by(sampleid, genus) %>% 
  summarise(cnt = sum(count)) %>% 
  # get the total count from the db to calculate the relab
  left_join(h %>% distinct(sampleid,count_total ), by = 'sampleid') %>% 
  mutate(relab = cnt/count_total) %>% 
  select(sampleid, genus, relab)

mcts_all %>% 
  write_csv('../data/amplicon/healthy_volunteer_genus_relab.csv')

h %>% 
  write_csv('../data/amplicon/healthy_volunteer_asv_relab.csv')
```

### 2021-04-14 scripts/56_rethinking_genera.Rmd
although slow but Im progressing

# plot them together in one 
bind_rows(
  res_top %>% mutate(grp = 'top'),
  res_bot %>% mutate(grp = 'bot')
) %>% 
  gghistogram(x = 'value',bins = 30, fill = 'grp', palette = 'nejm', color = 'white', add = 'mean',
                  xlab = 'Predicted probability of Toxicity', ylab = 'Probability density') +
  ggsave('../figs/predicted_tox_bacteroides_top_bottom_10.pdf', width = 7, height = 5)
```

@@

>>>>

# plot them together in one 
bind_rows(
  res_top %>% mutate(grp = 'top'),
  res_bot %>% mutate(grp = 'bot')
) %>% 
  gghistogram(x = 'value',bins = 30, fill = 'grp', palette = 'nejm', color = 'white', add = 'mean',
                  xlab = 'Predicted probability of Toxicity', ylab = 'Probability density') +
  ggsave('../figs/predicted_tox_bacteroides_top_bottom_10.pdf', width = 7, height = 5)

bind_rows(
  res_top %>% mutate(grp = 'top'),
  res_bot %>% mutate(grp = 'bot')
) %>% 
  group_by(grp) %>% 
  summarise(ave = mean(value))

@@

bind_rows(
  res_top %>% mutate(grp = 'top'),
  res_bot %>% mutate(grp = 'bot')
)  %>% 
  group_by(grp) %>% 
  summarise(ave = mean(value))
```
